Associations_PFN_Cognition

### 2022-08-31 Step1_TotalCorticalRepresentation/Associations_PFN_Cognition.Rmd
Step1_TotalCorticalRepresentation

---
title: "ABCD_Flux22_PFN_Analyses"
author: "Arielle Keller"
date: "3/21/2022"
output: html_document
---

@@

library(devtools)
install_github("jfortin1/neuroCombatData")
install_github("jfortin1/neuroCombat_Rpackage")
library(neuroCombat)
```

@@

# Remove subjects based on the following criteria:
## 1) 8min of retained TRs (600 TRs)
## 2) ABCD Booleans for rest and T1
```{r}
num_TRs <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/num_TRs_by_subj_redo.csv")
data<-merge(pfn_sizes,num_TRs,by="subjectkey")
data.clean<-data[data$numTRs>=600,] # we go from 9,132 to 8,293 at this step

# Remove participants based on booleans from ABCD
abcd_imgincl01 <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/abcd_imgincl01.csv")
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$eventnam=="baseline_year_1_arm_1",]
abcd_imgincl01 <- abcd_imgincl01[!abcd_imgincl01$visit=="",] # start here with 11,663 (8,287 of the 9,132 set)
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_t1w_include==1,] # down to 11,124 (8,045 of the 9,132 set)
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_rsfmri_include==1,] # down to 9,388 (7,475 of the 9,132 set)

combined.data <- merge(data.clean,abcd_imgincl01[, c("subjectkey",'imgincl_t1w_include')],by="subjectkey") # n=7,475
```

## Instead of calculating the Thompson factor scores ourselves, use the summary scores from DEAP
```{r}
newdata<-readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/DEAP-data-download_ThompsonScores_ResFamIncome.rds")
newdata.baseline<-newdata[newdata$event_name=="baseline_year_1_arm_1",]
colnames(newdata.baseline)[1]<-"subjectkey"
all.data <- merge(combined.data,newdata.baseline[,c("subjectkey", setdiff(colnames(newdata.baseline),colnames(combined.data)))],by="subjectkey")

# for simplicity, rename thompson variables
colnames(all.data)<-gsub("neurocog_pc1.bl","thompson_PC1",colnames(all.data))
colnames(all.data)<-gsub("neurocog_pc2.bl","thompson_PC2",colnames(all.data))
colnames(all.data)<-gsub("neurocog_pc3.bl","thompson_PC3",colnames(all.data)) # still at n=7,475
```

# Add in Family and Site covariates
```{r}
family <-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/ses/acspsw03.txt",header=TRUE)
family.baseline<-family[family$eventname=="baseline_year_1_arm_1",]
abcd.data.almost <- merge(all.data,family.baseline[, c("subjectkey", setdiff(colnames(family.baseline),colnames(all.data)))],by="subjectkey")
site_info <- readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/DEAP-siteID.rds")
site.baseline<-site_info[site_info$event_name=="baseline_year_1_arm_1",]
colnames(site.baseline)[1]<-"subjectkey"
abcd.data.almost2 <- merge(abcd.data.almost,site.baseline[,c("subjectkey", setdiff(colnames(site.baseline),colnames(abcd.data.almost)))],by="subjectkey") # n=7,474
```

# Add mean FD
```{r}
meanFD <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/PFN_Gradients_CombinedScript/getFD/meanFD_031822.csv")
colnames(meanFD)<-c("subjectkey","meanFD")
meanFD$subjectkey <- gsub(pattern="sub-NDAR",replacement="NDAR_", meanFD$subjectkey)
abcd.data <- merge(abcd.data.almost2,meanFD,by="subjectkey")

# n=7,461
```

# Load train/test split from UMinn
```{r}
traintest<-read_tsv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/participants.tsv")
traintest.baseline<-traintest[traintest$session_id=="ses-baselineYear1Arm1",c("participant_id","matched_group")]
colnames(traintest.baseline)[1]<-c("subjectkey")
traintest.baseline$subjectkey <- gsub(pattern="sub-NDAR",replacement="NDAR_", traintest.baseline$subjectkey)
traintest.baseline<-traintest.baseline %>% distinct()
abcd.data.traintest <- merge(abcd.data,traintest.baseline,by="subjectkey")
abcd.data.train <- abcd.data.traintest[abcd.data.traintest$matched_group==1,] # n=3,749
abcd.data.test <- abcd.data.traintest[abcd.data.traintest$matched_group==2,] # n=3,712
```

@@

# harmonize TEST set 
batch <- abcd.data.test$abcd_site
abcd.data.test.toharmonize <- abcd.data.test[,c("PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17","thompson_PC1","thompson_PC2","thompson_PC3","meanFD")]
mod <- model.matrix(~abcd.data.test$interview_age+abcd.data.test$sex+abcd.data.test$rel_family_id)
dat <- t(abcd.data.test.toharmonize)
abcd.data.combat <- neuroCombat(dat=dat,mod=mod,batch=batch,eb=FALSE)
dat.harmonized<-data.frame(t(abcd.data.combat$dat.combat))
abcd.data.noPFNsCog <- subset(abcd.data.test,select=-c(PFN1,PFN2,PFN3,PFN4,PFN5,PFN6,PFN7,PFN8,PFN9,PFN10,PFN11,PFN12,PFN13,PFN14,PFN15,PFN16,PFN17,thompson_PC1,thompson_PC2,thompson_PC3,meanFD))
abcd.data.test.harmonized <- cbind(abcd.data.noPFNsCog,dat.harmonized) # Add the harmonized data back into the main dataframe (BE AWARE THAT NOT ALL DATA IS HARMONIZED)

@@

# quick  analyses for flux abstract
```{r}
summary(lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
summary(lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
summary(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))

@@

# Make a demographics table
```{r}
# exclude n=488 subjects with missing cognitive data
abcd.data.for.ridge<-abcd.data.traintest[,c("subjectkey","thompson_PC1","thompson_PC2","thompson_PC3","matched_group","interview_age","sex","meanFD","abcd_site","rel_family_id")]

@@

### Replicate Cui bar graph:
```{r}
pfn1<-summary(lmer(PFN1~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn2<-summary(lmer(PFN2~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn3<-summary(lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized)) 
pfn4<-summary(lmer(PFN4~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn5<-summary(lmer(PFN5~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized)) 
pfn6<-summary(lmer(PFN6~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn7<-summary(lmer(PFN7~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized)) 
pfn8<-summary(lmer(PFN8~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn9<-summary(lmer(PFN9~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn10<-summary(lmer(PFN10~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn11<-summary(lmer(PFN11~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn12<-summary(lmer(PFN12~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn13<-summary(lmer(PFN13~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn14<-summary(lmer(PFN14~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn15<-summary(lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn16<-summary(lmer(PFN16~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn17<-summary(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))

@@

z_vec_pn <- z_vec*pos_neg
keep_p <- ifelse(p_vec_adj<.05,1,0)

@@

### Replicate Cui bar graph (SAME THING IN TEST SET):
```{r}
pfn1<-summary(lmer(PFN1~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn2<-summary(lmer(PFN2~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn3<-summary(lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized)) 
pfn4<-summary(lmer(PFN4~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn5<-summary(lmer(PFN5~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized)) 
pfn6<-summary(lmer(PFN6~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn7<-summary(lmer(PFN7~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized)) 
pfn8<-summary(lmer(PFN8~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn9<-summary(lmer(PFN9~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn10<-summary(lmer(PFN10~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn11<-summary(lmer(PFN11~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn12<-summary(lmer(PFN12~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn13<-summary(lmer(PFN13~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn14<-summary(lmer(PFN14~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn15<-summary(lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn16<-summary(lmer(PFN16~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn17<-summary(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))

@@

z_vec_pn <- z_vec*pos_neg
keep_p <- ifelse(p_vec_adj<.05,1,0)

@@

## Replicate Cui result showing topography across-individual variability by network
```{r}

# library(R.matlab)
# library(ggplot2);
# 
# ResultsFolder = '/data/jux/BBL/projects/pncSingleFuncParcel/Replication/Revision';
# AtlasFolder = paste0(ResultsFolder, '/SingleParcellation/SingleAtlas_Analysis');
# Variability_Visualize_Folder = paste0(AtlasFolder, '/Variability_Visualize');
# Variability_Mat = readMat(paste0(Variability_Visualize_Folder, '/VariabilityLoading_Median_17SystemMean.mat'));
# 
# AtlasLabel_Mat = readMat(paste0(AtlasFolder, '/Group_AtlasLabel.mat'));
# 
# AllData = data.frame(Variability = matrix(0, 17734, 1));
# AllData$Label = matrix(0, 17734, 1);
# for (i in c(1:17734))
# {
#   AllData$Variability[i] = Variability_Mat$VariabilityLoading.Median.17SystemMean.NoMedialWall[i];
#   AllData$Label[i] = AtlasLabel_Mat$sbj.AtlasLabel.NoMedialWall[i];
# }
# AllData$Variability = as.numeric(AllData$Variability);
# AllData$Label = as.factor(AllData$Label);
# 
# # Order the network by the median value
# MedianValue = matrix(0, 1, 17);
# for (i in c(1:17)) {
#   ind = which(AllData$Label == i);
#   MedianValue[i] = median(AllData$Variability[ind]);
# }
# # Store network variability for correlation with effect size
# writeMat(paste0(ResultsFolder, '/Corr_NetworkVariability_EffectSize/NetworkVariability.mat'), MedianValue = MedianValue);
# tmp = sort(MedianValue, index.return = TRUE);
# 
# ColorScheme = c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
#                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
#                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E",
#                 "#4E31A8", "#F5BA2E");
# ColorScheme_XText = c("#AF33AD", "#AF33AD", "#7499C2", "#7499C2", "#4E31A8",
#                 "#7499C2", "#7499C2", "#F5BA2E", "#00A131", "#E76178",
#                 "#E443FF", "#E443FF", "#E76178", "#E76178", "#F5BA2E",
#                 "#00A131", "#F5BA2E");
# Order = c(10, 6, 4, 2, 16, 11, 13, 15, 5, 12, 7, 9, 8, 1, 17, 14, 3);
# ColorScheme_XText_New = ColorScheme_XText;
# for (i in c(1:17)) {
#   ind = which(Order == i);
#   ColorScheme_XText_New[ind] = ColorScheme_XText[i];
# }
# ggplot(AllData, aes(x = Label, y = Variability, fill = Label, color = Label)) + 
#       geom_violin(trim = FALSE) +
#       scale_color_manual(values = ColorScheme) + 
#       scale_fill_manual(values = ColorScheme) + 
#       labs(x = "Networks", y = "Across-subject Variability") + theme_classic() +
#       theme(axis.text.x = element_text(size = 22, color = ColorScheme_XText_New),
#             axis.text.y = element_text(size = 22, color = "black"),
#             axis.title = element_text(size = 22)) +
#       theme(axis.text.x = element_text(angle = 22, hjust = 1)) + 
#       theme(legend.position = "none") + 
#       scale_x_discrete(
#             limits = c(10, 6, 4, 2, 16, 11, 13, 15, 5, 12, 7, 9, 8, 1, 17, 14, 3),
#             labels = c("12", "11", "2", "6", "14", "7", "8", "17", "16", "9", 
#                        "13", "5", "15", "10", "3", "1", "4")) + 
#       geom_boxplot(width=0.1, fill = "white");
# ggsave('/data/jux/BBL/projects/pncSingleFuncParcel/Replication/Revisioni/Figures/Variability_Loading_Mean_Violin.tiff', width = 20, height = 15, dpi = 600, units = "cm");

>>>>

---
title: "Associations_PFN_Cognition"
author: "Arielle Keller"
date: "3/21/2022"
output: html_document
---

@@

library(devtools)
install_github("jfortin1/neuroCombatData")
install_github("jfortin1/neuroCombat_Rpackage")
library(neuroCombat)

library(R.matlab)
library(mgcv)
library(ggplot2)
library(visreg)
library(ggtext)
```

@@

# Remove subjects based on the following criteria:
## 1) 8min of retained TRs (600 TRs)
## 2) ABCD Booleans for rest and T1
```{r}
num_TRs <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/num_TRs_by_subj_redo.csv")
data<-merge(pfn_sizes,num_TRs,by="subjectkey")
data.clean<-data[data$numTRs>=600,]

# Remove participants based on booleans from ABCD
abcd_imgincl01 <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/abcd_imgincl01.csv")
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$eventnam=="baseline_year_1_arm_1",]
abcd_imgincl01 <- abcd_imgincl01[!abcd_imgincl01$visit=="",] 
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_t1w_include==1,]
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_rsfmri_include==1,]

combined.data <- merge(data.clean,abcd_imgincl01[, c("subjectkey",'imgincl_t1w_include')],by="subjectkey") 
```

## Import the Thompson PC scores from DEAP
```{r}
newdata<-readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/DEAP-data-download_ThompsonScores_ResFamIncome.rds")
newdata.baseline<-newdata[newdata$event_name=="baseline_year_1_arm_1",]
colnames(newdata.baseline)[1]<-"subjectkey"
all.data <- merge(combined.data,newdata.baseline[,c("subjectkey", setdiff(colnames(newdata.baseline),colnames(combined.data)))],by="subjectkey")

# for simplicity, rename thompson variables
colnames(all.data)<-gsub("neurocog_pc1.bl","thompson_PC1",colnames(all.data))
colnames(all.data)<-gsub("neurocog_pc2.bl","thompson_PC2",colnames(all.data))
colnames(all.data)<-gsub("neurocog_pc3.bl","thompson_PC3",colnames(all.data))
```

# Add in Family and Site covariates
```{r}
family <-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/ses/acspsw03.txt",header=TRUE)
family.baseline<-family[family$eventname=="baseline_year_1_arm_1",]
abcd.data.almost <- merge(all.data,family.baseline[, c("subjectkey", setdiff(colnames(family.baseline),colnames(all.data)))],by="subjectkey")
site_info <- readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/DEAP-siteID.rds")
site.baseline<-site_info[site_info$event_name=="baseline_year_1_arm_1",]
colnames(site.baseline)[1]<-"subjectkey"
abcd.data.almost2 <- merge(abcd.data.almost,site.baseline[,c("subjectkey", setdiff(colnames(site.baseline),colnames(abcd.data.almost)))],by="subjectkey") 
```

# Add mean FD
```{r}
meanFD <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/PFN_Gradients_CombinedScript/getFD/meanFD_031822.csv")
colnames(meanFD)<-c("subjectkey","meanFD")
meanFD$subjectkey <- gsub(pattern="sub-NDAR",replacement="NDAR_", meanFD$subjectkey)
abcd.data <- merge(abcd.data.almost2,meanFD,by="subjectkey")
```

# Load discovery/replication matched samples 
```{r}
traintest<-read_tsv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/participants.tsv")
traintest.baseline<-traintest[traintest$session_id=="ses-baselineYear1Arm1",c("participant_id","matched_group")]
colnames(traintest.baseline)[1]<-c("subjectkey")
traintest.baseline$subjectkey <- gsub(pattern="sub-NDAR",replacement="NDAR_", traintest.baseline$subjectkey)
traintest.baseline<-traintest.baseline %>% distinct()
abcd.data.traintest <- merge(abcd.data,traintest.baseline,by="subjectkey")
abcd.data.traintest<-abcd.data.traintest[!duplicated(abcd.data.traintest$subjectkey),] # remove duplicated subject
abcd.data.train <- abcd.data.traintest[abcd.data.traintest$matched_group==1,] 
abcd.data.test <- abcd.data.traintest[abcd.data.traintest$matched_group==2,] 
```

@@

# harmonize TEST set 
batch <- abcd.data.test$abcd_site
abcd.data.test.toharmonize <- abcd.data.test[,c("PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17","thompson_PC1","thompson_PC2","thompson_PC3","meanFD")]
mod <- model.matrix(~abcd.data.test$interview_age+abcd.data.test$sex+abcd.data.test$rel_family_id)
dat <- t(abcd.data.test.toharmonize)
abcd.data.combat <- neuroCombat(dat=dat,mod=mod,batch=batch,eb=FALSE)
dat.harmonized<-data.frame(t(abcd.data.combat$dat.combat))
abcd.data.noPFNsCog <- subset(abcd.data.test,select=-c(PFN1,PFN2,PFN3,PFN4,PFN5,PFN6,PFN7,PFN8,PFN9,PFN10,PFN11,PFN12,PFN13,PFN14,PFN15,PFN16,PFN17,thompson_PC1,thompson_PC2,thompson_PC3,meanFD))
abcd.data.test.harmonized <- cbind(abcd.data.noPFNsCog,dat.harmonized) # Add the harmonized data back into the main dataframe

@@

# linear mixed effects models associating general cognition with each fronto-parietal PFN
```{r}
summary(lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
summary(lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
summary(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))

@@

# Make a demographics table
```{r}
# exclude subjects with missing cognitive data
abcd.data.for.ridge<-abcd.data.traintest[,c("subjectkey","thompson_PC1","thompson_PC2","thompson_PC3","matched_group","interview_age","sex","meanFD","abcd_site","rel_family_id")]

@@

### Bar plot (Discovery Sample):
```{r}
pfn1<-summary(lmer(PFN1~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn2<-summary(lmer(PFN2~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn3<-summary(lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized)) 
pfn4<-summary(lmer(PFN4~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn5<-summary(lmer(PFN5~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized)) 
pfn6<-summary(lmer(PFN6~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn7<-summary(lmer(PFN7~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized)) 
pfn8<-summary(lmer(PFN8~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn9<-summary(lmer(PFN9~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn10<-summary(lmer(PFN10~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn11<-summary(lmer(PFN11~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn12<-summary(lmer(PFN12~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn13<-summary(lmer(PFN13~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn14<-summary(lmer(PFN14~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn15<-summary(lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn16<-summary(lmer(PFN16~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn17<-summary(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))

@@

z_vec_pn_train <- z_vec*pos_neg
keep_p <- ifelse(p_vec_adj<.05,1,0)

z_vec_sorted = rank(z_vec_pn_train);

# Using 7 colors scheme for bar plot
# bar plot for cognition effects
data <- data.frame(CognitionEffects_Z = as.numeric(z_vec_pn_train)) 
data$EffectRank <- as.numeric(z_vec_sorted)
BorderColor <- c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E", 
                 "#4E31A8", "#F5BA2E");
LineType <- c("dashed", "solid", "solid", "solid", "dashed", "dashed",
              "dashed", "dashed", "dashed", "dashed", "dashed", "dashed",
              "dashed", "dashed", "solid", "dashed", "solid");
Fig <- ggplot(data, aes(EffectRank, CognitionEffects_Z)) +
  geom_bar(stat = "identity", fill=c("#FFFFFF", "#7499C2", "#F5BA2E",
                                     "#7499C2", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF",
                                     "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF",
                                     "#FFFFFF", "#F5BA2E", "#FFFFFF", "#F5BA2E"), 
           colour = BorderColor, linetype = LineType, width = 0.8) + 
  labs(x = "Networks", y = expression(paste("Cognition Association (", italic("Z"), ")"))) + theme_classic() +
  theme(axis.text.x = ggtext::element_markdown(size= 27, color = BorderColor[c(4,2,11,10,1,9,5,16,14,12,7,8,13,6,3,15,17)]), 
        axis.text.y = ggtext::element_markdown(size= 33, color = "black"), 
        axis.title=ggtext::element_markdown(size = 33)) +
  theme(axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1)) +
  scale_x_discrete(labels = c('4','2','11','10','1','9','5','16','14','12','7','8','13','6','3','15','17'),limits = c('5','2','15','1','7','14','11','12','6','4','3','10','13','9','16','8','17')) 
Fig
ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/NetworkSize_Loading_CogEffects.tiff', width = 19, height = 16, dpi = 600, units = "cm");

@@

### Bar plot (Replication Sample):
```{r}
pfn1<-summary(lmer(PFN1~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn2<-summary(lmer(PFN2~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn3<-summary(lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized)) 
pfn4<-summary(lmer(PFN4~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn5<-summary(lmer(PFN5~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized)) 
pfn6<-summary(lmer(PFN6~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn7<-summary(lmer(PFN7~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized)) 
pfn8<-summary(lmer(PFN8~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn9<-summary(lmer(PFN9~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn10<-summary(lmer(PFN10~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn11<-summary(lmer(PFN11~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn12<-summary(lmer(PFN12~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn13<-summary(lmer(PFN13~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn14<-summary(lmer(PFN14~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn15<-summary(lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn16<-summary(lmer(PFN16~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn17<-summary(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))

@@

z_vec_pn_test <- z_vec*pos_neg
keep_p <- ifelse(p_vec_adj<.05,1,0)

z_vec_sorted = rank(z_vec_pn_test);

# Using 7 colors scheme for bar plot
# bar plot for cognition effects
data <- data.frame(CognitionEffects_Z = as.numeric(z_vec_pn_test)) 
data$EffectRank <- as.numeric(z_vec_sorted)
BorderColor <- c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E", 
                 "#4E31A8", "#F5BA2E");
LineType <- c("dashed", "dashed", "solid", "solid", "dashed", "solid",
              "dashed", "dashed", "dashed", "dashed", "dashed", "dashed",
              "dashed", "dashed", "solid", "dashed", "solid");
Fig <- ggplot(data, aes(EffectRank, CognitionEffects_Z)) +
  geom_bar(stat = "identity", fill=c("#FFFFFF", "#FFFFFF", "#F5BA2E",
                                     "#7499C2", "#FFFFFF", "#AF33AD", "#FFFFFF", "#FFFFFF",
                                     "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF",
                                     "#FFFFFF", "#F5BA2E", "#FFFFFF", "#F5BA2E"), 
           colour = BorderColor, linetype = LineType, width = 0.8) + 
  labs(x = "Networks", y = expression(paste("Cognition Association (", italic("Z"), ")"))) + theme_classic() +
  theme(axis.text.x = ggtext::element_markdown(size= 27, color = BorderColor[c(4,13,9,2,7,12,10,5,16,14,8,1,11,3,15,17,6)]), 
        axis.text.y = ggtext::element_markdown(size= 33, color = "black"), 
        axis.title=ggtext::element_markdown(size = 33)) +
  theme(axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1)) +
  scale_x_discrete(labels = c('4','13','9','2','7','12','10','5','16','14','8','1','11','3','15','17','6'),limits = c('12','4','14','1','8','17','5','11','3','7','13','6','2','10','15','9','16')) # + scale_y_continuous(limits = c(-4, 6), breaks = c(-4, -2, 0, 2, 4, 6));
Fig
ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/NetworkSize_Loading_CogEffects_test.tiff', width = 19, height = 16, dpi = 600, units = "cm");

@@
